The Kapowski Chronicles: A Complete, Volumetric Cortical Thickness Open Source Pipeline with Evaluation on Public Data

### 2013-03-25 KapowskiChronicles/methods.tex
ENH: Ozzy

>>>>

In order to better integrate Atropos and N4, we use  
a pure tissue probability weight mask generated from the 
posterior probabilities generated by the segmentation 
process.  Given $N$ labels and the corresponding $N$
posterior probability maps $\{ P_1, \ldots, P_N\}$ produced
during the segmentation process, the N4 weight mask is 
created at each N4 $\Leftrightarrow$ Atropos iteration from:
\begin{align}
  P_{pure\,\,tissue}(\mathbf{x}) = \sum_{i=1}^N P_i(\mathbf{x}) \prod_{j=1, j \neq i}^N \left( 1 - P_j(\mathbf{x}) \right).
\end{align}
